---
title: "Data and Programming Structures"
author: "Jay"
date: "17/09/2019"
output:
  ioslides_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Expression

Write $2 + \sqrt{4} + ln(e^2) + 2^2$ as an R expression and get its result.

```{r}
# an expression
2 + sqrt(4) + log(exp(2)) + 2^2
```

## Assignment

Assign an expression to a variable using the assignment operator, `<-`.

```{r}
# assignment
x <- (pi == 3.14)
print(x)
```

## Data Structure

| Dimension | Homogeneous   | Heterogeneous |
|:---------:|:-------------:|:-------------:|
| 1D        | Atomic vector | List          |
| 2D        | Matrix        | Dataframe     |
| nD        | Array         | -             |


## Atomic Vector

```{r}
# create R vectors
vec_character <- c("Hello,", "World!")
vec_integer <- c(1L, 2L, 3L)
vec_double <- c(1.1, 2.2, 3.3, -4.4)
vec_logical <- c(TRUE, TRUE, FALSE)
```

## Retrieve a Single Element

```{r}
# retrieve the first element of vec_double
print(vec_double[1])
```

## Retrieve Multiple Elements - 1

```{r}
# select multiple elements
print(vec_double[c(1, 3)])
print(vec_double[1:2])
print(vec_double[c(-1, -2)])
```

## Retrieve Multiple Elements - 2

```{r}
# select multiple elements
print(vec_double[c(TRUE, FALSE, TRUE, FALSE)])
print(vec_double[vec_double < 0])